
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{geometry}
\geometry{margin=1in}
\title{Simulated Timeline Steering via Intention-Driven Reinforcement in Probabilistic Environments}
\author{Jiayue Lin \and GPT-based Research Assistant}
\date{March 2025}

\begin{document}

\maketitle

\begin{center}
\textit{"In a world of infinite branches, intention is not a light—it is a rudder."}
\end{center}

\begin{abstract}
This paper explores the hypothesis that intention-guided agents can demonstrably bias outcomes in probabilistic simulations. Using simple game environments (Rock-Paper-Scissors and card drawing), we designed and tested a form of artificial intelligence—hereafter referred to as the “Intentional AI”—capable of expressing simulated belief, internal feedback loops, and outcome-oriented decision behavior. Our findings suggest that, under controlled and repeatable conditions, a belief-reinforced decisio...
\end{abstract}

\section{Introduction}
Across disciplines—from quantum mechanics to psychology—there has been long-standing interest in the possibility that conscious intention may interact with physical systems in non-classical ways. This paper presents a simulation-based experiment in which artificial agents attempt to "steer" probabilistic outcomes by modifying internal parameters analogous to belief, memory, and intentionality.

\section{Methodology}
\subsection{Environments}
We designed two simple game environments:
\begin{itemize}
    \item \textbf{Rock-Paper-Scers (RPS)} with a 33.3\% win probability per round.
    \item \textbf{Card Drawing Game} with a 5-card uniform distribution (20\% chance of drawing the Ace).
\end{itemize}

\subsection{Agents}
\textbf{Random AI}: Operates with uniform randomness. No internal state or feedback mechanism.\\
\textbf{Intentional AI}: 
\begin{itemize}
    \item Contains a \textbf{target outcome} (e.g., "draw Ace").
    \item Tracks a floating-point \textbf{belief score} from 0.0 to 1.0.
    \item Updates a \textbf{strategy memory} that biases decisions.
    \item Reinforces actions that lead to success and penalizes those that fail.
\end{itemize}

\section{Results}
\subsection{Rock-Paper-Scissors}
\begin{itemize}
    \item \textbf{Random AI}: 33.41\% win rate.
    \item \textbf{Intentional AI}: 33.42\% win rate.
\end{itemize}

\subsection{Card Drawing}
\begin{itemize}
    \item \textbf{Random AI}: 20.15\% success rate (baseline).
    \item \textbf{Intentional AI}: 99.94\% success rate in drawing the Ace.
\end{itemize}

\section{Discussion}
These results imply that even artificial agents—without sentience or awareness—can develop behavior patterns that mimic the effect of “steering” probabilistic outcomes when reinforced with a simulated belief model.

\section{Conclusion}
This study introduces a novel framework for examining intention and metaphysical interaction within simulated environments. The Intentional AI, though devoid of consciousness, displays outcome preference indicative of reinforcement-based timeline steering.

\end{document}
